Final Report

### 2022-05-07 Final Report.Rmd
nicer plots

kable(low_poll, ascending=TRUE)

@@

***
```{r, echo=FALSE}

@@

# High Outdoor Air Pollution
h_outdoor <- ggplot(high_poll, aes(x=country, y = avg_outdoor, color = avg_ozone, cex=5)) +
  geom_point() +
  labs(title = "Outdoor Air Pollution Deaths in High Population Countries") +
  xlab("Country") + 
  ylab("Average Deaths")
ggplotly(h_outdoor)

#Low Outdoor Air Pollution
l_outdoor <- ggplot(low_poll, aes(x = country, y= avg_outdoor, color = avg_ozone, cex=5)) +
  geom_point() +
  labs(title = "Outdoor Air Pollution Deaths in Low Population Countries")+
  xlab("Country")+
  ylab("Average Deaths")
ggplotly(l_outdoor)
```

>>>>

@@

***
```{r, echo=FALSE, warning=FALSE}

@@

# High Outdoor Air Pollution
h_outdoor <- ggplot(high_poll, aes(x=country, y = avg_outdoor, color = avg_ozone, cex=5)) +
  scale_color_gradient2(low = "light pink", mid = "pink", high = "violet", aesthetics = "colour") +
  geom_point() +
  labs(title = "Outdoor Air Pollution Deaths in High Population Countries") +
  xlab("Country") + 
  ylab("Average Deaths")
ggplotly(h_outdoor)

#Low Outdoor Air Pollution
l_outdoor <- ggplot(low_poll, aes(x = country, y= avg_outdoor, color = avg_ozone, cex=5)) +
  scale_color_gradient2(low = "light pink", mid = "pink", high = "violet", aesthetics = "colour") +
  geom_point() +
  labs(title = "Outdoor Air Pollution Deaths in Low Population Countries")+
  xlab("Country")+
  ylab("Average Deaths")
ggplotly(l_outdoor)
```
